Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-02-28 paper.tex
removed mentions to a new paradigm (evaluate later)

The goals of the present article is to briefly present part of the established research and also clarify the current trends, given that we are on the verge of a paradigm shift, mainly driven by CPSs and IoT. We present a brief discussion about models for CPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding the verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section \ref{Newapp} then addresses new applications, which take into account the new paradigm mentioned here, and Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems. Finally, we conclude and describe future work in Section~\ref{conclusions}.

>>>>

The goals of the present article is to briefly present part of the established research and also clarify the current trends, which are mainly driven by CPSs and IoT. We present a brief discussion about models for CPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding the verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section \ref{Newapp} then addresses new applications, which take into account the new trends mentioned here, and Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems. Finally, we conclude and describe future work in Section~\ref{conclusions}.
